---
title: " "
output:
  pdf_document
geometry: "left = 1.5in, right = 1in, top = 1in, bottom = 1in"
fontsize: 12pt
linestretch: 2
header-includes:
  - \usepackage{float}
  - \usepackage{sectsty}
  - \usepackage{paralist}
  - \usepackage{setspace}\spacing{2}
  - \usepackage{fancyhdr}
  - \usepackage{lastpage}
  - \usepackage{dcolumn}
  - \usepackage{natbib}
  - \bibliographystyle{agsm}
  - \usepackage[nottoc, numbib]{tocbibind}
  - \usepackage{pdflscape}
  - \usepackage{longtable}
  - \usepackage{subcaption}
  - \usepackage{grffile}
  - \usepackage{chngcntr}
  - \usepackage{sectsty}
  - \usepackage{changepage}
  - \usepackage[normalem]{ulem}
  - \useunder{\uline}{\ul}{}
  - \usepackage{tocloft}

bibliography: 
  - "../../references/bibliography.bib"
biblio-style: "apacite"
link-citations: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\renewcommand*\contentsname{TABLE OF CONTENTS} 
\renewcommand*\listfigurename{LIST OF FIGURES} 
\renewcommand*\listtablename{LIST OF TABLES}

\allsectionsfont{\centering\normalsize\fontsize{12pt}{12}}
\subsectionfont{\raggedright}
\subsubsectionfont{\raggedright}

\pagenumbering{gobble}

\begin{large}
    \begin{center}
      \mbox{}
      \vfill
      {\MakeUppercase{Development of Decision Strategies under Risk and Uncertainty}}\\
      \vfill
      A Dissertation Proposal Presented\\
      by \\
      \MakeUppercase{Ramiro Eduardo Rea Reyes}\\
      \vfill
      Committee:\\
      Youngbin Kwak, Chair\\
      Kirby Deater-Deckard, Member\\
      Jeffrey Starns, Member\\
      Elena Vazey, Member\\
      \vfill
      Neuroscience and Behavior Program\\
    	\vfill
      \vspace*{.2in}
    \end{center}
\end{large}

\newpage

\begin{titlepage}
  \begin{center}
    {\MakeUppercase{Development of Decision Strategies under Risk and Uncertainty}}\\
    Dissertation Proposal by \\
    \MakeUppercase{Ramiro Eduardo Rea Reyes}\\
    June 12, 2023
  \end{center}
  \begin{tabular}{l}
    \\Approved as to style and content by:\\
    \makebox[2.5in]{\hrulefill}\\
    {Youngbin Kwak, Chair}\\
    \makebox[2.5in]{\hrulefill}\\
    {Kirby Deater-Deckard, Member}\\
    \makebox[2.5in]{\hrulefill}\\
    {Jeffrey Starns, Member}\\
    \makebox[2.5in]{\hrulefill}\\
    {Elena Vazey, Member}\\
  \end{tabular}\hfill
    
  \begin{tabular}[t]{@{}r@{}}
    \makebox[2.5in]{\hrulefill}\\
    \rightline{Luke Remage-Healey, Graduate Program Director}\\
    Neuroscience and Behavior Program\\
  \end{tabular}
\end{titlepage}

\newpage

\pagenumbering{roman}

\centering
\raggedright
\newpage

\renewcommand\cftsecfont{\mdseries}
\renewcommand\cftsecpagefont{\mdseries}

\tableofcontents
\addtocontents{toc}{~\hfill\text{Page}\par}

\newpage

\listoftables
\addtocontents{lot}{Table\hfill\text{Page}\par}

\newpage

\listoffigures
\addtocontents{lof}{Figure\hfill\text{Page}\par}

\allsectionsfont{\fontsize{12}{12}\selectfont}

\addtocontents{toc}{~\par}
\addtocontents{toc}{CHAPTER\par}

\newpage

\pagenumbering{arabic}

\allsectionsfont{\centering\normalsize\fontsize{12pt}{12}}
\subsectionfont{\raggedright}
\subsubsectionfont{\raggedright}

\section{I. BACKGROUND AND SIGNIFICANCE}
```{r background, child='chapter_01_background.Rmd'}

```

\newpage
\section{II. STUDY 1: EYE-TRACKING ANALYSIS OF HEURISTIC-DRIVEN INFORMATION SEARCH IN UNCERTAIN DECISION ENVIRONMENTS}
```{r heuristics-uncertainty, child='chapter_02_heuristics-under-uncertainty.Rmd'}

```

\newpage
\section{III. STUDY 2: EFFECTS OF DEVELOPMENT ON HEURISTIC STRATEGIES USE UNDER UNCERTAINTY}
```{r heuristics-development, child='chapter_03_heuristics-through-development.Rmd'}

```

\newpage
\section{IV. STUDY 3: DISENTANGLING INFORMATION PROCESSING DURING MOTOR DECISIONS UNDER RISK}
```{r heuristics-risk, child='chapter_04_heuristics-under-risk.Rmd'}

```

\clearpage

```{r biblio, child = 'bibliography.Rmd'}
```

\newpage
\addtocontents{toc}{APPENDICES\par}
\section{A. PARAMETERS AND EQUATIONS FOR ANALYSIS REPORTED IN CHAPTER II}
```{r appendix-a, child='appendix_a.Rmd'}

```

\newpage
\section{B. PARAMETERS AND EQUATIONS FOR ANALYSIS REPORTED IN CHAPTER III}
```{r appendix-b, child='appendix_b.Rmd'}

```

\newpage
\section{C. PARAMETERS AND EQUATIONS FOR ANALYSIS REPORTED IN CHAPTER IV}
```{r appendix-c, child='appendix_c.Rmd'}

```