---
title: " "
output:
  pdf_document
geometry: "left = 1.5in, right = 1in, top = 1in, bottom = 1in"
fontsize: 12pt
linestretch: 2
header-includes:
  - \usepackage{float}
  - \usepackage{sectsty}
  - \usepackage{paralist}
  - \usepackage{setspace}\spacing{2}
  - \usepackage{fancyhdr}
  - \usepackage{lastpage}
  - \usepackage{dcolumn}
  - \usepackage{natbib}
  - \bibliographystyle{agsm}
  - \usepackage[nottoc, numbib]{tocbibind}
  - \usepackage{pdflscape}
  - \usepackage{longtable}
  - \usepackage{subcaption}
  - \usepackage{grffile}
  - \usepackage{chngcntr}
  - \usepackage{sectsty}
  - \usepackage{changepage}
  - \usepackage[normalem]{ulem}
  - \useunder{\uline}{\ul}{}


bibliography: 
  - "bibliography.bib"
biblio-style: "apacite"
link-citations: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\renewcommand*\contentsname{TABLE OF CONTENTS} 
\renewcommand*\listfigurename{LIST OF FIGURES} 
\renewcommand*\listtablename{LIST OF TABLES}

\allsectionsfont{\centering\normalsize\fontsize{12pt}{12}}
\subsectionfont{\raggedright}
\subsubsectionfont{\raggedright}

\pagenumbering{gobble}

\begin{large}
    \begin{center}
      \mbox{}
      \vfill
      Development of Decision Strategies under Risk and Uncertainty\\
      \vfill
      A Dissertation Proposal Presented\\
      by \\
      \MakeUppercase{Ramiro Eduardo Rea Reyes}\\
      \vfill
      Committee:\\
      Youngbin Kwak, Chair\\
      Kirby Deater-Deckard, Member\\
      Jeffrey Starns, Member\\
      Elena Vazey, Member\\
      \vfill
      Neuroscience and Behavior Program\\
    	\vfill
      \vspace*{.2in}
    \end{center}
\end{large}

\newpage

\pagenumbering{roman}

\centering
\raggedright
\newpage
\tableofcontents
\addtocontents{toc}{~\hfill\text{Page}\par}

\newpage

\listoftables
\addtocontents{lot}{Table\hfill\text{Page}\par}

\newpage

\listoffigures
\addtocontents{lof}{Figure\hfill\text{Page}\par}

\allsectionsfont{\fontsize{12}{12}\selectfont}

\addtocontents{toc}{~\par}
\addtocontents{toc}{CHAPTER\par}

\newpage

\pagenumbering{arabic}


\allsectionsfont{\centering\normalsize\fontsize{12pt}{12}}
\subsectionfont{\raggedright}
\subsubsectionfont{\raggedright}


```{r background, child='chapter_01_background.Rmd'}

```

\newpage
```{r heuristics-uncertainty, child='chapter_02_heuristics-under-uncertainty.Rmd'}

```

\newpage
```{r heuristics-development, child='chapter_03_heuristics-through-development.Rmd'}

```

\newpage
```{r heuristics-risk, child='chapter_04_heuristics-under-risk.Rmd'}

```

\clearpage

```{r biblio, child = 'bibliography.Rmd'}
```

\newpage
\addtocontents{toc}{APPENDIX\par}

```{r appendix-a, child='supplementary_A_equations.Rmd'}

```

\newpage
```{r appendix-b, child='supplementary_B_equations.Rmd'}

```

\newpage
```{r appendix-c, child='supplementary_C_equations.Rmd'}

```